Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-06-07 manuscript/manuscript.Rmd
Switching to lighter/yellower green

train_test_levels <- c("MS3000-MS3000", "FT2040-FT2040", "MS3000-FT2040", "FT2040-MS3000")
train_test_labels <- c("MESO-MESO", "Falkor-Falkor", "MESO-Falkor", "Falkor-MESO")
fdr_gff_cross_train_gp <- fdr_gff_cross_train_df %>%
  pivot_longer(c(FDR, GFF)) %>%
  mutate(name=paste0("%", name)) %>%
  mutate(which_params=factor(which_params, 
                             labels=c("All metrics", "XCMS metrics", "Raw data metrics"),
                             levels=c("all_params", "xcms_params", "raw_data_params"))) %>%
  mutate(cross_type_num=as.numeric(cross_type)) %>%
  mutate(train_test=factor(train_test, levels=train_test_levels, labels=train_test_labels)) %>%
  mutate(name=factor(name, levels=c("%GFF", "%FDR"), labels=c("GFF", "FDR"))) %>%
  ggplot() +
  geom_point(aes(x=cross_type, y=value, color=train_test, 
                 fill=train_test, shape=name), size=5) +
  geom_smooth(aes(x=cross_type_num, y=value, group=name), 
              method = "lm", formula="y~x", color="black", se=FALSE) +
  facet_grid(~which_params) +
  scale_x_discrete(labels = c("Same\ndataset\n", "Different\ndataset\n"),
                   breaks = c("Same", "Different")) +
  scale_color_manual(values = c("#0b505c", "#184d1f", "#0d8299", "#028e34"), 
                     breaks = train_test_labels,
                     aesthetics = c("color", "fill")) +
  scale_shape_manual(breaks = c("GFF", "FDR"), values = c("\u25B2", "\u25BC")) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_bw() +
  theme() +
  labs(x=NULL, y=NULL, color="Train-test", fill="Train-test", shape="Error type") +
  guides(shape=guide_legend(order=1))

@@

fdr_gff_cross_train_df_fancy <- net_cross_train_df %>%
  rbind(rf_cross_train_df) %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  drop_na() %>%
  group_by(train_test, which_alpha, cross_type) %>%
  count(error_type) %>%
  ungroup() %>%
  mutate(cross_type=factor(cross_type, levels=c("Same", "Different"))) %>%
  pivot_wider(names_from=error_type, values_from = n, values_fill = 0) %>%
  mutate(FDR=FP/(FP+TP)) %>%
  mutate(GFF=TP/(FN+TP)) %>%
  mutate(cross_type_num=as.numeric(cross_type))
train_test_levels <- c("MS3000-MS3000", "FT2040-FT2040", "MS3000-FT2040", "FT2040-MS3000")
train_test_labels <- c("MESO-MESO", "Falkor-Falkor", "MESO-Falkor", "Falkor-MESO")
fdr_gff_cross_train_gp <- fdr_gff_cross_train_df_fancy %>%
  mutate(train_test=factor(train_test, levels=train_test_levels, labels=train_test_labels)) %>%
  mutate(which_alpha=factor(which_alpha, levels=c("ridge", "elastic", "lasso", "rf"),
                            labels=c("Ridge: α=0", "Elastic: α=0.5", "Lasso: α=1", "Random forest"))) %>%
  pivot_longer(c(FDR, GFF)) %>%
  ggplot() +
  geom_smooth(aes(x=cross_type_num, y=value, group=name), 
              method = "lm", formula="y~x", color="black", se=FALSE) +
  geom_point(aes(x=cross_type, y=value, color=train_test, 
                 fill=train_test, shape=name), size=5, alpha=0.8) +
  facet_grid(~which_alpha) +
  scale_x_discrete(labels = c("Same\ndataset\n", "Different\ndataset\n"),
                   breaks = c("Same", "Different")) +
  scale_color_manual(values = c("#0b505c", "#184d1f", "#0d8299", "#028e34"), 
                     breaks = train_test_labels,
                     aesthetics = c("color", "fill")) +
  scale_shape_manual(breaks = c("GFF", "FDR"), values = c("\u25B2", "\u25BC")) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_bw() +
  theme() +
  labs(x=NULL, y=NULL, color="Train-test", fill="Train-test", shape="Error type") +
  guides(shape=guide_legend(order=1))

>>>>

train_test_levels <- c("MS3000-MS3000", "FT2040-FT2040", "MS3000-FT2040", "FT2040-MS3000")
train_test_labels <- c("MESO-MESO", "Falkor-Falkor", "MESO-Falkor", "Falkor-MESO")
fdr_gff_cross_train_gp <- fdr_gff_cross_train_df %>%
  pivot_longer(c(FDR, GFF)) %>%
  mutate(name=paste0("%", name)) %>%
  mutate(which_params=factor(which_params, 
                             labels=c("All metrics", "XCMS metrics", "Raw data metrics"),
                             levels=c("all_params", "xcms_params", "raw_data_params"))) %>%
  mutate(cross_type_num=as.numeric(cross_type)) %>%
  mutate(train_test=factor(train_test, levels=train_test_levels, labels=train_test_labels)) %>%
  mutate(name=factor(name, levels=c("%GFF", "%FDR"), labels=c("GFF", "FDR"))) %>%
  ggplot() +
  geom_point(aes(x=cross_type, y=value, color=train_test, 
                 fill=train_test, shape=name), size=5) +
  geom_smooth(aes(x=cross_type_num, y=value, group=name), 
              method = "lm", formula="y~x", color="black", se=FALSE) +
  facet_grid(~which_params) +
  scale_x_discrete(labels = c("Same\ndataset\n", "Different\ndataset\n"),
                   breaks = c("Same", "Different")) +
  scale_color_manual(values = c("#0b505c", "#3A601E", "#0d8299", "#028e34"), 
                     breaks = train_test_labels,
                     aesthetics = c("color", "fill")) +
  scale_shape_manual(breaks = c("GFF", "FDR"), values = c("\u25B2", "\u25BC")) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_bw() +
  theme() +
  labs(x=NULL, y=NULL, color="Train-test", fill="Train-test", shape="Error type") +
  guides(shape=guide_legend(order=1))

@@

fdr_gff_cross_train_df_fancy <- net_cross_train_df %>%
  rbind(rf_cross_train_df) %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  drop_na() %>%
  group_by(train_test, which_alpha, cross_type) %>%
  count(error_type) %>%
  ungroup() %>%
  mutate(cross_type=factor(cross_type, levels=c("Same", "Different"))) %>%
  pivot_wider(names_from=error_type, values_from = n, values_fill = 0) %>%
  mutate(FDR=FP/(FP+TP)) %>%
  mutate(GFF=TP/(FN+TP)) %>%
  mutate(cross_type_num=as.numeric(cross_type))
train_test_levels <- c("MS3000-MS3000", "FT2040-FT2040", "MS3000-FT2040", "FT2040-MS3000")
train_test_labels <- c("MESO-MESO", "Falkor-Falkor", "MESO-Falkor", "Falkor-MESO")
fdr_gff_cross_train_gp <- fdr_gff_cross_train_df_fancy %>%
  mutate(train_test=factor(train_test, levels=train_test_levels, labels=train_test_labels)) %>%
  mutate(which_alpha=factor(which_alpha, levels=c("ridge", "elastic", "lasso", "rf"),
                            labels=c("Ridge: α=0", "Elastic: α=0.5", "Lasso: α=1", "Random forest"))) %>%
  pivot_longer(c(FDR, GFF)) %>%
  ggplot() +
  geom_smooth(aes(x=cross_type_num, y=value, group=name), 
              method = "lm", formula="y~x", color="black", se=FALSE) +
  geom_point(aes(x=cross_type, y=value, color=train_test, 
                 fill=train_test, shape=name), size=5, alpha=0.8) +
  facet_grid(~which_alpha) +
  scale_x_discrete(labels = c("Same\ndataset\n", "Different\ndataset\n"),
                   breaks = c("Same", "Different")) +
  scale_color_manual(values = c("#0b505c", "#3A601E", "#0d8299", "#028e34"), 
                     breaks = train_test_labels,
                     aesthetics = c("color", "fill")) +
  scale_shape_manual(breaks = c("GFF", "FDR"), values = c("\u25B2", "\u25BC")) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_bw() +
  theme() +
  labs(x=NULL, y=NULL, color="Train-test", fill="Train-test", shape="Error type") +
  guides(shape=guide_legend(order=1))
